---
title: "Experiment 1: Feeding Behaviour Sucrose Consumption"
author: "Claire"
date: "March 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Packages

```{r libraries, message = FALSE}
library(tidyverse)
library(readxl)
library(lmerTest)
library(emmeans)
library(performance)
library(dplyr)
library(Rmisc)
```

#' Import data and check structure
```{r}
sucrose <- read_excel("DataGit/FeedingBehaviour.xlsx", sheet="Sucrose") %>%
  pivot_longer(cols = starts_with("Day "),
               names_to = "Day",
               names_prefix = "Day ",
               values_to = "sucrose") %>%
  mutate(Day = factor(Day, levels = c(1,2,3,4,5,6,7,8,9,10)))
```
#' ## Visualise data
```{r}
ggplot(sucrose, aes(Day, sucrose, col = Treatment)) +
  geom_boxplot() 
```
#' Remove largest value, likely error, and re-run
```{r}
sucrose %>%
  filter(sucrose <0.3) %>%
  ggplot(sucrose, mapping = aes(Day, sucrose, colour = Treatment)) +
  geom_boxplot()
```
#' Pretty Version
```{r}
ggplot(sucrose, aes(Day, sucrose, colour = Treatment)) +
  geom_boxplot() + coord_cartesian(ylim=c(0,0.25)) +
  ggtitle("Sucrose Consumption") + labs(y="Consumption per bee (mg)", x="Day")
```
#' Visualise by Day
```{r}
ggplot(sucrose, aes(Treatment, sucrose, colour = Treatment)) +
  geom_point() +
  facet_wrap(~Day) +theme_bw() + theme(axis.text.x = element_text(angle = 90))
```
#' ## Fit movel to data
#' lm model with and without Day effect
```{r}
slm1 <- lm(sucrose~Treatment + factor(Cage), data=sucrose)
summary(slm1)
slm2 <- lm(sucrose~Treatment*Day + factor(Cage), data=sucrose)
summary(slm2)
anova(slm1, slm2)
```
# Using the Linear Mixed Modelling - Lmer
#' lmr compare with and without time effect
```{r}
slmer1<- lmer(sucrose~Treatment*Day + (1|Cage), data = sucrose)
slmer2<- lmer(sucrose~Treatment + (1|Cage), data = sucrose)
anova(slmer1, slmer2)
```
#' Lmer Model with Day as an interaction 
```{r}
slmer1<- lmer(sucrose~Treatment*Day + (1|Cage), data = sucrose)
summary(slmer1)
anova(slmer1)
```

#' lmer model assumptions   
```{r}
check_model(slmer1)
```

#' lmer result

# lmer model means and SE
```{r}
emmeans(slmer1, ~Treatment|Day)
sresult1 <- summary(emmeans(slmer1,~Treatment|Day))
```

#Summary statistics from model in plot
```{r}
ggplot(sresult1, aes(x=Treatment, y=emmean, colour = Treatment)) +
  geom_point()+
  geom_errorbar(aes(ymax = emmean+SE, ymin = emmean-SE), width = .3)+
  facet_wrap(~Day) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))
```
#' lmer model means and SE looking at effect of Day
```{r}
emmeans(slmer1, ~Day|Treatment)
sresult2 <- summary(emmeans(slmer1,~Day*Treatment))
```

#'
```{r}

ggplot(sresult2, aes(x=Treatment, y=emmean, colour = Treatment)) +
  geom_point()+
  geom_errorbar(aes(ymax = emmean+SE, ymin = emmean-SE), width = .3)+
  facet_wrap(~Day) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))
```



