---
title: "Experiment 1: Feeding Behaviour Pollen Consumption"
author: "Claire"
date: "March 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Packages

```{r libraries, message = FALSE}
library(tidyverse)
library(readxl)
library(lmerTest)
library(emmeans)
library(performance)
library(dplyr)
library(Rmisc)
```

#' Import data and check structure

```{r}
pollen <- read_excel("DataGit/FeedingBehaviour.xlsx", sheet="Pollen") %>%
  pivot_longer(cols = starts_with("Day "),
               names_to = "Day",
               names_prefix = "Day ",
               values_to = "pollen") %>%
  mutate(Day = factor(Day, levels = c(2,3,4,5,6,7,8,9,10)))
str(pollen)
```
#' Visualise data - First Plot
```{r}
ggplot(pollen, aes(Day, pollen, col = Treatment)) +
  geom_boxplot()
```
#' Visualize Data
```{r}
ggplot(pollen, aes(Day, pollen, col = Treatment)) +
    geom_boxplot(size=0.5, width=1) + coord_cartesian(xlim=c(0,10), ylim=c(0,0.020)) + 
    ggtitle("Pollen Consumption") + labs(y="Consumption per bee (mg)", x="Day")
```
## Observations

## Visualise by Day
```{r}
ggplot(pollen, aes(Treatment, pollen, col = Treatment)) +
  geom_point() +
  facet_wrap(~Day) +theme_bw() + theme(axis.text.x = element_text(angle = 90))
```
#' Visualise 
```{r}
ggplot(pollen, aes(Day, pollen, col = Treatment)) +
  geom_point() +
  facet_wrap(~Treatment) +theme_bw() + theme(axis.text.x = element_text(angle = 90))
```
## plot
```{r}
ggplot(pollen, aes(x = Day, y = pollen, colour = factor(Cage)))+
  geom_line(aes(group=Cage))+
  facet_wrap(~Treatment)+
  theme(legend.position = "top")
```


## Fit an analysis of Variance Model
## Fit model to data - Looking for things impacting residuals
```{r}
treatment <- lm(pollen ~ Treatment, data = pollen)
Cage <- lm(pollen ~ Cage, data = pollen)
Day <- lm(pollen ~ Day, data = pollen)
anova(treatment)
anova(Cage)
anova(Day)
```
## Observations
## Testing each variable with a one-way ANOVA of the lm model has shown only 
# Day to have a significant Pr(>F) value
# This is consistent with the visual trend shown in first plot

## Day must be accounted for as interaction from here
##' lm model with (lm2) and without cage effect (lm1)
```{r}
lm1 <- lm(pollen~Treatment*Day, data=pollen)
  lm2 <- lm(pollen~Treatment*Day + factor(Cage), data=pollen)
  anova(lm1)
  anova(lm2)
  anova(lm1, lm2)
```
# This seems to suggest that adding cage as a factor is significant
  
##' lmr compare with and without time effect
```{r}
lmer1<- lmer(pollen~Treatment*Day + (1|Cage), data = pollen)
  lmer2<- lmer(pollen~Treatment + (1|Cage), data = pollen)
  anova(lmer1, lmer2)
```
#significant difference with and without time effect as expected
  
# Now we know what need to be in our Linear Mixed model
```{r}
  lmer1<- lmer(pollen~Treatment*Day + (1|Cage), data = pollen)
  summary(lmer1)
  anova(lmer1)
```
#' lmer model assumptions   
```{r}
check_model(lmer1)
```

#' lmer result
#' Data looks pretty good, no issues in homoscendascity test, the model is not missing any relationships

#' lmer model means and SE
```{r}
emmeans(lmer1, ~Treatment|Day)
result1 <- summary(emmeans(lmer1,~Treatment|Day))
```
#Summary statistics from model in plot
```{r}
ggplot(presult1, aes(x=Treatment, y=emmean, colour = Treatment)) +
  geom_point()+
  geom_errorbar(aes(ymax = emmean+SE, ymin = emmean-SE), width = .3)+
  facet_wrap(~Day) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))
```
#' lmer model means and SE looking at effect of Day
```{r}
emmeans(lmer1, ~Day|Treatment)
result2 <- summary(emmeans(lmer1,~Day*Treatment))
```
#
```{r}
ggplot(result2, aes(x=Treatment, y=emmean, colour = Treatment)) +
  geom_point()+
  geom_errorbar(aes(ymax = emmean+SE, ymin = emmean-SE), width = .3)+
  facet_wrap(~Day) +
  theme_bw() + theme(axis.text.x = element_text(angle = 90)) + 
  ggtitle("Pollen Consumption of Lmer Model") + labs(y="Consumption per bee (mg)")
```

