---
title: "Experiment 2: Cycle 2 Survival Data"
author: "Claire"
date: "March 2021"
output: html_document
---

## Cycle 2 6 days of survival data - file "SurvivaldataCycle2R"
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Packages

```{r libraries, message = FALSE}
library(readr)
library(tidyverse)
library(emmeans)
library(dplyr)
library(Rmisc)
library(glmmTMB)
library(car)
library(lmerTest)
library(ggResidpanel)
```

## Import data and check data structure

```{r import_data, message = FALSE}
C2R <- read_csv("DataGit/SurvivalDataCycle2R.csv")
str(C2R)
```

## Data Structure
##Reponse variable 
#= Percent_survived: Percent of individual bees alive at time point, cage specific based on total number of bees alive at start of treatment
##Factors 
#= Day: Survival data collected over a 6 day period
#= Treatment: 4 levels of treatments - Control, High_Copper, Low_Copper, No_microbiome
#= Cage: 4 Cages as replicate per treatment, numbered 1-4

##Visualize Data
#Initial plot = Seperated by treatment with each cage coloured
```{r check_observations}
ggplot(C2R, aes(x = day, y = percent_survived, colour = factor(cage)))+
  geom_line(aes(group=cage))+
  facet_wrap(~treatment)+
  theme(legend.position = "top")
```  
#Observations
(1) Cage variation within Treatments
(2) Once cage starts reducing in numbers, continues at faster rate - Experimental design
(3) All Treatments remain steady for the first few days then follow a downward pattern in survival with time 

## Summary Statistics
```{r}
StatsC2R <- summarySE(C2R, measurevar="percent_survived", groupvars=c("treatment","day"))
```

## First Plot Grouping by Treatment - Cages pooled
```{r}
ggplot(data=StatsC2R, aes(x=day, y=percent_survived, group = treatment, colour = treatment)) + geom_line() + geom_point()
```
# Plot with Error Bars
```{r}
ggplot(data=StatsC2R, aes(x=day, y=percent_survived, group = treatment, colour = treatment)) +
  geom_errorbar(aes(ymin=percent_survived-se, ymax=percent_survived+se)) +
  geom_errorbar(aes(ymin=percent_survived-sd, ymax=percent_survived+sd), width=.3, size=1.1) +
  geom_line()
```
# Plot with Standard Error
```{r}
ggplot(data=StatsC2R, aes(x=day, y=percent_survived, group = treatment, colour = treatment)) +
  geom_errorbar(aes(ymin=percent_survived-se, ymax=percent_survived+se)) +
  geom_line() + geom_point()
```
## Data Exploration - Plot by Treatment/Cage
```{r}
ggplot(StatsC1R, aes(x = day, y = percent_survived, colour = treatment))+
  facet_wrap(~treatment)+
  theme(legend.position = "top")+
  geom_errorbar(aes(ymin=percent_survived-se, ymax=percent_survived+se), width=0.5, size=0.5) +
  geom_point(size=3) + geom_line(size=1)
```
## Fit model 
```{r}
modC2 <- glmmTMB(cbind(alive,dead)~treatment*day + (1|cage:treatment), data = C2R, family = binomial(link = "logit"))
```
## ANOVA Table
```{r}
Anova(modC2)
```
# Descibe the effects

## Assess model assumptions with residual plots
```{r model_assessment}
resid_panel(modC2)
```
