---
title: "QiimeDataGenusboxplot"
author: "Claire"
date: "19/11/2021"
output: html_document
---

```{r library}
# Load packages 
# > Cut the ones I didnt use
library(DECIPHER)
library(DESeq2)
library(gridExtra)
library(ggnewscale) 
library(ggpubr)
library(ggthemes)
library(grid) 
library(vegan)
library(phyloseq)
library(png)
library(qgraph) 
library(ggsignif)
library(RColorBrewer)
library(tidyverse)
library(ggplot2)
library(dabestr)
library(ranacapa)
```


TRYING TO DO JUST CYCLE 1 First to see if I can run it.
But if you want to run both cycles together then just change the metadata.txt import to metafileBothCycles.csv Ive added another coloumn known as cycle - cycle_one or cycle_two







## Importing from Qiime
# Import data from Qiime - feature table, OTU and taxonomy files
# Make OTU ID the row names

```{r}
Tab <- read.delim("DataGit/feature_table_new.txt")
colnames(Tab)  <- gsub("\\.", "-", colnames(Tab))
row.names(Tab)<-Tab[[1]]
write.table(Tab, file="Tab", sep='\t',col.names=TRUE, row.names=FALSE)
```

#Import in taxonomy
#Open in excel, delete D_0__ etc with replace function
```{r}
taxonomy<- read.delim("DataGit/biom-taxonomy2.tsv")
names(taxonomy) <- c("X-OTU-ID", "tax", "Confidence")
row.names(taxonomy) <-taxonomy[[1]]
taxonomy <- taxonomy[,(-3)]
taxonomy <-  separate(taxonomy, tax, c("D0","D1", "D2", "D3", "D4", "D5", "D6","D7"), sep = ";", fill = "right")
taxonomy <- taxonomy[,c(1:8)]
write.table(taxonomy, file="taxonomy_new", sep='\t',col.names=TRUE, row.names=FALSE)
```
#Save as taxonomy2.csv
```{r}
taxonomy=read.csv("DataGit/taxonomy2.csv",sep=",",row.names=1)
taxonomy <- cbind(taxonomy, ASV = paste0("ASV", sprintf("%04d", 1:nrow(taxonomy))))
taxonomy=as.matrix(taxonomy)
```
#Import in otu table
```{r}
otu_table=read.csv("DataGit/Svtab_new2edit.csv",sep=",",row.names=1)
otu_table=as.matrix(otu_table)
```
#Import the metatable
#View (metatable) to check 
```{r}
metatable <- read.delim("DataGit/metadata.txt") 
row.names(metatable) <- metatable[[1]]
metatable<- metatable[,(-1)]
META <- sample_data(metatable)
```
#Import taxonomy, otu table and metadata as phyloseq objects
#Check that all are TRUE
```{r}
OTU=otu_table(otu_table,taxa_are_rows=TRUE)
TAX=tax_table(taxonomy)
sample_names(META) == sample_names(OTU)
```

#Create phyloseq object of the phyoseq data
#Change the taxonomy header to Names instead of Dnumber
#Check names are correct
```{r}
Genus<- phyloseq(OTU, TAX, META)
Genus<- phyloseq(OTU, TAX, META)
colnames(tax_table(Genus)) <- c(D0 = "Kingdom", D1 = "Phylum", D2 = "Class", 
                              D3 = "Order", D4 = "Family", D5 = "Genus", D6 = "Species", ASV = "ASV")
rank_names(Genus)
```
#Check the length of the taxa - total number of ASVs
```{r}
length(taxa_names(Genus))
```

#Filter phyloseq object to only include Bacteria, exclude Choloplast and Mitochondria from samples
```{r}
library("phyloseq")
tog1 = subset_taxa(Genus, Kingdom =="Bacteria")
tog1 <- prune_taxa(taxa_sums(tog1) > 0, tog1)
tog1<-subset_taxa(tog1, (Order!="Chloroplast"))
tog1<-subset_taxa(tog1, (Family!="Mitochondria"))
```
#Length check - reduces total taxa numbers from 1004 to 961 (minus 43)
```{r}
length(taxa_names(tog1))
```

CYCLE 1 ONLY - SIG NOT WORKING

Genus boxplot
```{r total abundance}
total <-Genus
total <-rarefy_even_depth(total,sample.size=5404, replace=FALSE, rngseed = 1)
total <- subset_samples(total, sampling_time != "Cycle 2")
total <- subset_samples(total, sampling_time != "Mock DNA")
sample_data(total)$treatment<-factor(sample_data(total)$treatment,levels=c("Control","High_Copper","Low_Copper"))
total <- prune_taxa(taxa_sums(total) > 0, total)
total <- tax_glom(total, taxrank = 'Genus')
total = subset_taxa(total, Genus=="Lactobacillus" | Genus=="Bartonella" | Genus=="Gilliamella" | Genus=="Snodgrassella" | Genus=="Frischella" | Genus=="Bifidobacterium" | Genus=="Commensalibacter")
```

#Melt and plot

```{r}
tot<-psmelt(total)
neworder3 <- c("Bartonella","Lactobacillus","Gilliamella","Snodgrassella","Bifidobacterium","Commensalibacter","Frischella")
library(plyr)
tot <- arrange(transform(tot, Genus=factor(Genus,levels=neworder3)),Genus)
a_mean <- tot %>%
  group_by(Genus) %>%
  summarize(mean_val = mean(Abundance))
```

```{r}
G<-ggplot(data = tot, aes(x = treatment, y = Abundance))+geom_boxplot(aes(fill=Genus),alpha=0.5,lwd=0.7, position = position_dodge(width = 0.3), width=0.45,outlier.shape = NA) + geom_jitter(aes(color = Genus), height = 0, width = .1)+geom_hline(data= a_mean, aes(yintercept=mean_val), width=5,size=1,linetype="dashed")+
  labs(x = "", y = "Abundance\n")+theme_bw()+facet_grid(Genus~treatment, scales = "free")
```

```{r}
sigFunc = function(x){
  if(x < 0.001){"***"}
  else if(x < 0.01){"**"}
  else if(x < 0.05){"*"}
  else{NA}}
G<-G+theme_bw()+
  geom_signif(comparisons=list(c("Control", "Low_copper")),tip_length = 0.03,vjust=1.3, color="grey20", size=1.1,map_signif_level=sigFunc, textsize=9, test = wilcox.test,step_increase = 0.2)
print(G)
```




TESTING TO MAKE PLOT WITH BOTH CYCLES 

Barplots
## Core taxa abundance
```{r total abundance}
tog <-tog1
tog <- rarefy_even_depth(tog,sample.size=5404, replace=FALSE, rngseed = 1)
tog=subset_samples(sampling_time != "Mock DNA")
sample_data(tog)$treatment<-factor(sample_data(Comm)$treatment,levels=c("Control","High_Copper","Low_Copper"))
tog <- prune_taxa(taxa_sums(tog) > 0, tog)
tog <- tax_glom(tog, taxrank = 'Genus')
tog = subset_taxa(tog, Genus=="Lactobacillus" | Genus=="Bartonella" | Genus=="Gilliamella" | Genus=="Snodgrassella" | Genus=="Frischella" | Genus=="Bifidobacterium" | Genus=="Commensalibacter")


#Melt and plot
mtog<-psmelt(tog)
levels2=c("cycle_one","cycle_two")
change <- c("Cycle one","Cycle two")
melt2 <- arrange(transform(melt2, cycle=factor(cycle,levels=levels2,labels=change)),cycle)
neworder3 <- c("Bartonella","Lactobacillus","Gilliamella","Snodgrassella","Bifidobacterium","Commensalibacter","Frischella")
melt4 <- arrange(transform(melt2, Genus=factor(Genus,levels=neworder3)),Genus)
a_mean <- melt4 %>%
  group_by(treatment3,Genus,cycle) %>%
  summarize(mean_val = mean(Abundance))
a_mean2<-subset(a_mean, treatment3 =="Control")
print(a_mean2)
sigFunc = function(x){
  if(x < 0.001){"***"}
  else if(x < 0.01){"**"}
  else if(x < 0.05){"*"}
  else{NA}}
p<-ggplot(data = melt4, aes(x = treatment3, y = Abundance)) +
  geom_boxplot(aes(fill=Genus),alpha=0.5,lwd=0.7, position = position_dodge(width = 0.3), width=0.45,outlier.shape = NA) + geom_jitter(aes(color = Genus), height = 0, width = .1)+geom_hline(data= a_mean2, aes(yintercept=mean_val), width=5,size=1,linetype="dashed")+
  labs(x = "", y = "Abundance\n")+
  facet_grid(Genus~cycle, scales = "free")+theme_bw()+
  geom_signif(comparisons=list(c("Control", "Low_copper")),tip_length = 0.03,vjust=1.3, color="grey20", size=1.1,map_signif_level=sigFunc, textsize=9, test = wilcox.test,step_increase = 0.2)
p<-p+ theme(legend.position="right")+ylab("Total abundance")
p<-p+ theme(legend.text=element_text(size=29, face = "italic"))+theme(legend.key = element_rect(color = NA, fill = NA),legend.key.size = unit(0.9, "cm"))+theme(legend.title = element_blank())
abu<-p +theme(strip.text.x = element_text(size=25,face="bold",color = "grey 35"))+theme(strip.background =element_rect(fill="white", color="white"))
cycle<-abu+theme(axis.title.y = element_text(size=25, face="bold"))+theme(axis.text.y = element_text(size=20, face="bold"))+theme(axis.text.x = element_text(size=25, angle=90,face="bold"))+theme(axis.title.x = element_blank())+ theme(strip.text.y = element_blank())
```








